### 2011-08-02 doc/theses/svirec/appendixA.tex
some fixes

The CD is a part of this thesis. It contains text of this thesis, source code of jInfer framework with \texttt{FDRepairer} extension together with documentation and built jInfer as \texttt{nbm} plugins applicable into NetBeans platform. It aslo contains experimental data and results. CD has the following structure:

>>>>

The CD is a part of this thesis. It contains text of this thesis, source code of jInfer framework with \texttt{FDRepairer} module together with documentation and built jInfer as \texttt{nbm} plugins applicable into NetBeans platform. It aslo contains experimental data and results. CD has the following structure:

### 2011-08-02 doc/theses/svirec/kap3.tex
some fixes

\begin{define}[Repair]
Given an XML tree $T$, a DTD $D$ and a set of integrity constraints $IC$ (Definition \ref{integConstr}), a set of update operations $R$ is said to be a {\sl repair} of $T$ (with respect to $D$ and $IC$) if $R(T) \models IC$, where $R(T)$ is application of consistent set of updates $R$ to $T$, $R(T)$ conforms $D$ and $\not \exists R' \sqsubset R$ such that $R'(T) \models IC$ and $R'(T)$ conforms $D$.
\end{define}

@@

\begin{algorithm}[H]
\caption{Fix-Initial-Conflicts}
\label{fixInit}
\begin{algorithmic}[1]
\REQUIRE An XML document T, a set $\Sigma$ of FDs.
\ENSURE A modified document T.
\STATE \COMMENT Create the initial conflict hypergraph $g$ of $T$ w.r.t $\Sigma$
\STATE \COMMENT Use a known algorithm to find an approximation $VC$ for the minimum weighted vertex cover of $g$
\STATE $remaining$ := VC
\WHILE{there are two target nodes $v_1, v_2 \in T$ violating a FD $\sigma \in \Sigma$, and $v_1[\![P_{n+1}]\!]$ or $v_2[\![P_{n+1}]\!]$ is the only node in VC from the set of nodes $\{v_1[\![P_i]\!](i \in [1, n+1])\} \cup \{v_2[\![P_i]\!](i \in [1, n+1])\}$. (W.l.o.g assume the violation is as follows: $\sigma = (P,P',(P_1,\dots,P_n \rightarrow P_{n+1}))$, $v \in \{[\![P]\!]\}$, $v_1, v_2 \in \{v[\![P']\!]\}$, $v_1[\![P_i]\!] \equiv v_2[\![P_i]\!]$ for all $i \in [1,n]$, and $v_1[\![P_{n+1}]\!] \not \equiv v_2[\![P_{n+1}]\!]$.)}
\STATE $val(v_1[\![P_{n+1}]\!])$ := $val(v_2[\![P_{n+1}]\!])$ \COMMENT W.l.o.g, we assume $v_1[\![P_{n+1}]\!]$ is in VC
\ENDWHILE
\FORALL{node $u \in remaining$}
\STATE $val(u)$ := $gen\_new\_value()$
\STATE \COMMENT Introduce new values to all the remaining nodes in VC
\ENDFOR
\end{algorithmic}
\end{algorithm}

>>>>

\begin{define}[Repair]
Given an XML tree $T$, a DTD $D$ and a set of integrity constraints $IC$ (Definition \ref{integConstr}), a set of update operations $R$ is said to be a {\sl repair} of $T$ (with respect to $D$ and $IC$) if $R(T) \models IC$, where $R(T)$ is application of consistent set of updates $R$ to $T$, $R(T)$ conforms $D$ and $\not \exists R' \sqsubset R$ such that $R'(T) \models IC$ and $R'(T)$ conforms $D$.\qed
\end{define}

@@

\begin{algorithm}
\caption{Fix-Initial-Conflicts}
\label{fixInit}
\begin{algorithmic}[1]
\REQUIRE An XML document T, a set $\Sigma$ of FDs.
\ENSURE A modified document T.
\STATE \COMMENT Create the initial conflict hypergraph $g$ of $T$ w.r.t $\Sigma$
\STATE \COMMENT Use a known algorithm to find an approximation $VC$ for the minimum weighted vertex cover of $g$
\STATE $remaining$ := VC
\WHILE{there are two target nodes $v_1, v_2 \in T$ violating a FD $\sigma \in \Sigma$, and $v_1[\![P_{n+1}]\!]$ or $v_2[\![P_{n+1}]\!]$ is the only node in VC from the set of nodes $\{v_1[\![P_i]\!](i \in [1, n+1])\} \cup \{v_2[\![P_i]\!](i \in [1, n+1])\}$. (W.l.o.g assume the violation is as follows: $\sigma = (P,P',(P_1,\dots,P_n \rightarrow P_{n+1}))$, $v \in \{[\![P]\!]\}$, $v_1, v_2 \in \{v[\![P']\!]\}$, $v_1[\![P_i]\!] \equiv v_2[\![P_i]\!]$ for all $i \in [1,n]$, and $v_1[\![P_{n+1}]\!] \not \equiv v_2[\![P_{n+1}]\!]$.)}
\STATE $val(v_1[\![P_{n+1}]\!])$ := $val(v_2[\![P_{n+1}]\!])$ \COMMENT W.l.o.g, we assume $v_1[\![P_{n+1}]\!]$ is in VC
\ENDWHILE
\FORALL{node $u \in remaining$}
\STATE $val(u)$ := $gen\_new\_value()$
\STATE \COMMENT Introduce new values to all the remaining nodes in VC
\ENDFOR
\end{algorithmic}
\end{algorithm}

### 2011-08-02 doc/theses/svirec/kap6.tex
thesis fixing
some fixes

In this chapter, experimental results of the \texttt{FDRepairer} extension of the jInfer framework are presented. Set of documents and functional dependencies have been provided as an input and results from the former algorithm have been compared with results from \texttt{FDRepairer}. Documents in provided datasets are split into real-world and synthetic XML documents.

@@

The second dataset is a set of actors of IMDB database obtained from the Niagara data source (\url{http://www.cs.wisc.edu/niagara/data.html}). The dataset consists of a set of authors, where for each author a set of movies he played in is listed. DTD of this dataset is shown in Fig. \ref{actorsDTD}. For this dataset, we defined FD as follows: For each two authors, which played in the movie with the same name, the year of release of this movie must be the same.

@@

\begin{figure}[H]
    \begin{verbatim}
        <!ELEMENT customers (country)>
        <!ELEMENT country (name,c_list)>
        <!ELEMENT name (#PCDATA)>
        <!ELEMENT c_list (customer)*>
        <!ELEMENT customer (no,phone,zip,city)>
        <!ELEMENT no (#PCDATA)>
        <!ELEMENT phone (#PCDATA)>
        <!ELEMENT zip (#PCDATA)>
        <!ELEMENT city (#PCDATA)>
    \end{verbatim}
    \caption{DTD of actors.xml}
    \label{synthDTD}
\end{figure}

>>>>

In this chapter, experimental results of the \texttt{FDRepairer} module of the jInfer framework are presented. Set of documents and functional dependencies have been provided as an input and results from the former algorithm have been compared with results from \texttt{FDRepairer}. Documents in provided datasets are split into real-world and synthetic XML documents.

@@

The second dataset is a set of actors of IMDB database obtained from the Niagara data source (\url{http://www.cs.wisc.edu/niagara/data.html}). The dataset consists of a set of authors, where for each author a set of movies he played in is listed. DTD of this dataset is shown in Fig. \ref{actorsDTD}. For this dataset, we defined FD as follows: \emph{For each two authors, which played in the movie with the same name, the year of release of this movie must be the same}.

@@

\begin{figure}[H]
    \begin{verbatim}
        <!ELEMENT customers (country)>
        <!ELEMENT country (name,c_list)>
        <!ELEMENT name (#PCDATA)>
        <!ELEMENT c_list (customer)*>
        <!ELEMENT customer (no,phone,zip,city)>
        <!ELEMENT no (#PCDATA)>
        <!ELEMENT phone (#PCDATA)>
        <!ELEMENT zip (#PCDATA)>
        <!ELEMENT city (#PCDATA)>
    \end{verbatim}
    \caption{DTD of customers.xml}
    \label{synthDTD}
\end{figure}
